---
title: Post-assessment publications
---




```{r}
library(RefManageR)
here::i_am("publists/02-assessment.qmd")

BibOptions(check.entries = FALSE, style = "markdown", cite.style = "authoryear",
           bib.style = "numeric", hyperlink = FALSE)
```

```{r}
a.step <- read.csv(here::here("input/assessment-step.csv"),header=F,as.is=T)
dois <- subset(a.step,V2=="post assessment")$V1
```


```{r,echo=FALSE,message=FALSE,warning=FALSE}
bib1 <- ReadBib(here::here("bibTeX","RLE-collection-DOI-download.bib"), check = FALSE)
NoCite(bib = bib1, doi=dois, .opts = list(hyperlink = FALSE))
```


## Post assessment publications

Publications that summarize assessment outcomes.


```{r results = "asis", echo = FALSE}
PrintBibliography(bib1, .opts = list(check.entries = FALSE, max.names=100, sorting = "ydnt"))
```

## Authors

```{r}
bib2 <- SearchBib(bib1,doi=dois)
rev(sort(table(unlist(lapply(bib2, function(x) x$author$family)))))
```

## old list

* DA Keith (2014) *Separating risks from values in setting priorities for plant community conservation* DOI:[10.1111/avsc.12112](http://doi.org/10.1111/avsc.12112)
 * DA Keith (2015) *Assessing and managing risks to ecosystem biodiversity* DOI:[10.1111/aec.12249](http://doi.org/10.1111/aec.12249)
 * TM Brooks, SHM Butchart, NA Cox, M Heath, C Hilton-Taylor, M Hoffmann, N Kingston, JP Rodríguez, SN Stuart, J Smart (2015) *Harnessing biodiversity and conservation knowledge products to track the Aichi Targets and Sustainable Development Goals* DOI:[10.1080/14888386.2015.1075903](http://doi.org/10.1080/14888386.2015.1075903)
 * D Juffe-Bignoli, TM Brooks, SHM Butchart, RB Jenkins, K Boe, M Hoffmann, A Angulo, S Bachman, M Böhm, N Brummitt, KE Carpenter, PJ Comer, N Cox, A Cuttelod, WRT Darwall, M Di Marco, LDC Fishpool, B Goettsch, M Heath, C Hilton-Taylor, J Hutton, T Johnson, A Joolia, DA Keith, PF Langhammer, J Luedtke, E Nic Lughadha, M Lutz, I May, RM Miller, MA Oliveira-Miranda, M Parr, CM Pollock, G Ralph, JP Rodríguez, C Rondinini, J Smart, S Stuart, A Symes, AW Tordoff, S Woodley, B Young, N Kingston (2016) *Assessing the Cost of Global Biodiversity and Conservation Knowledge* DOI:[10.1371/journal.pone.0160640](http://doi.org/10.1371/journal.pone.0160640)
 * D Gigante, ATR Acosta, E Agrillo, S Armiraglio, S Assini, F Attorre, S Bagella, G Buffa, L Casella, C Giancola, GP Giusso del Galdo, C Marcenò, G Pezzi, I Prisco, R Venanzoni, D Viciani (2018) *Habitat conservation in Italy: the state of the art in the light of the first European Red List of Terrestrial and Freshwater Habitats* DOI:[10.1007/s12210-018-0688-5](http://doi.org/10.1007/s12210-018-0688-5)
